ARGoS-Blockchain interface

### 2020-09-02 article.tex
upd

@@

\subsection{Requirements}
\begin{itemize}
\item Linux
\item Docker
\end{itemize}

\subsection{Installation: Blockchain module}
The very first time you run this code, it is required to create the
Docker image for the Ethereum nodes and initialize Docker Swarm as
follows:

\begin{verbatim}
git clone https://github.com/Pold87/ARGoS-Blockchain-interface
cd ARGoS-Blockchain-interface/ && cd geth/
sudo docker build -t mygeth .
sudo docker swarm init
\end{verbatim}

@@

\begin{verbatim}
git clone https://github.com/Pold87/robot-swarms-need-blockchain
cd robot-swarms-need-blockchain/
mkdir cmake/
cd cmake/
cmake ..
make
\end{verbatim}

Additionally, you have to set the variable \verb|DOCKERBASE| in the
file \verb|global_config.sh| to the full path where this repository is
located on your computer, for example:

@@

In order to be able to mine, you need to create the DAG datasets as
follows (the creates files require approximately 2~GB disk space and
the execution of the script can take take several minutes):

@@

\section{Run}
Usually, the network is created when a swarm robotics experiment is
started, using one of the start scripts in
\url{https://github.com/Pold87/robot-swarms-need-blockchain}.

@@

>>>>

\begin{abstract}

  This technical report documents the installation and use of the
  ARGoS-Blockchain interface. This interface allows for conducting
  experiments in the robot swarm simulator ARGoS and the smart
  contract blockchain framework Ethereum. The blockchain part uses the
  container software Docker in order to facilitate the installation
  and the parallelization of the blockchain nodes. The use of
  blockchain-based smart contracts provides a framework for managing
  security issues in robot swarms. The interface is a convenient way
  to prototype blockchain-based control software in robot
  swarms. Byzantine robots, that is, robots that behave in an
  unintended way can disrupt the swarm behavior. In this technical
  report, we detail the motivation, setup, and usage of the
  ARGoS-blockchain interface.

\end{abstract}

@@

The following setup steps describe the installation using Linux as
operating system.

\subsection{Requirements}
\begin{itemize}
\item Sufficient disk space (at least 16 GB)
\item Docker 
\item ARGoS\footnote{\url{https://github.com/ilpincy/argos3}} and the
  ARGoS e-puck robot
  plugin\footnote{\url{https://github.com/demiurge-project/argos3-epuck}}
  (carefully read the instructions on the respective respositories)
\end{itemize}

\subsection{Installation --- Module~1: Blockchain module}

1. First, obtain the source code for the blockchain module:

\begin{verbatim}
$ git clone https://github.com/Pold87/ARGoS-Blockchain-interface
\end{verbatim}

2. Then, you need to create the Docker image for the Ethereum nodes and
initialize Docker Swarm as follows. By default, the execution of
Docker commands requires root user privileges. To facilitate the
execution of Docker commands, it is possible to run Docker as non-root
user (i.e., without \texttt{sudo}) as follows (see
\url{https://docs.docker.com/engine/install/linux-postinstall/} for
more detailed instructions):

\begin{verbatim}
$ sudo groupadd docker
$ sudo usermod -aG docker $USER
\end{verbatim}

4. Then, create the Ethereum image.

\begin{verbatim}
$ cd ARGoS-Blockchain-interface/ && cd geth/
$ docker build -t mygeth .
$ docker swarm init
\end{verbatim}

5. Set the ARGoS folder in start_network.sh

TODO: Run script with NUMROBOTS=0

TODO: Change from python to python3 in Dockerfile

TODO: Download geth and put it into myowngeth/

TODO:

@@

1. Obtain the source code for the ARGoS module.

\begin{verbatim}
git clone https://github.com/Pold87/ARGoS-Blockchain-interface
\end{verbatim}

2. Compile the ARGoS code.
\begin{verbatim}
cd robot-swarms-need-blockchain/
mkdir build/
cd build/
cmake ..
make
\end{verbatim}

3. Set the variable \verb|DOCKERBASE| in the file
\verb|global_config.sh| to the full path where the Blockchain module
(Module 1) repository is located on your computer, for example:

@@

4. In order to be able to mine, you need to create the DAG datasets as
follows (the creates files require approximately 2~GB disk space and
the execution of the script can take take several minutes):

@@

\section{Run}

Usually, the network is created when a swarm robotics experiment is
started, using one of the start scripts in
\url{https://github.com/Pold87/robot-swarms-need-blockchain}.

@@

\section{Debugging}

First, check that the Docker container for the bootstrap node and the
individual containers for the robots are running:

\begin{verbatim}

\end{verbatim}

% Mention --no-trunc and how to access logs

\section{Usage}

The functions of the interface can be found in the file
\texttt{/interface/generic_interface.cpp}.

\begin{itemize}
\item \texttt{unlockAccount}: Unlock the coinbase account.
\item \texttt{startMining}: Start the mining process using one thread.
\item \texttt{stopMining}: Stop the mining process.
\item \texttt{addPeer}: Add a peer based on its enode.
\item \texttt{removePeer}: Add a peer based on its enode.
\item \texttt{scInterface}: 
\end{itemize}
